---
title: "ST403 Final Project"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ST403FinalProject)
```

  #Exchange

The exchange family of methods in this package aim to return exchange rates for given currencies and plot these exchange rates. 

 1.  Below is an example where USD is converted to GBP.

```{r}
100*exchange_rate("USD","GBP")
100*exchange_rate("USD","GBP","2022-11-01")
```
  We see here at the time of writing 100$ equates to roughly 82.91£ but on the first of November was 86.93£. Note the date format yyyy-mm-dd and also be aware the data is only available for last 180 days.
  
  2.  If looking to see overall trend between two currencies we can use *exchange_plot*
  
```{r,fig.width=5.5,fig.height=4}
exchange_plot("USD","GBP")
```
  
   The lines indicate the min,median and max for the given exchange rate. The current exchange rate is also given in the title
  
  3.
To access this data in the form of a data frame to do your own analysis use function *load_fx*

```{r}
df1<-load_fx(rates_list = c("EUR/USD","EUR/GBP","EUR/AUD","EUR/NZD"))
df1<-df1[order(df1$Date,df1$rate,df1$Index,decreasing = T),]
head(df1,n=8)
```


  
