---
title: "popr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{popr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.width = 7,
  fig.height = 5,
  fig.align = "center",
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ST403FinalProject)
```

## Introduction 

__ST403FinalProject__ is an R package which downloads the latest population data for all the countries in the world. It includes data from 2022, 2020, 2015, 2010, 2000, 1990, 1980 and 1970. It also includes geometry data on each of these countries. It performs basic modelling of said data, and creates nice plots of population differences over time. Three functions are provided:

  1. `load_popr()`: for loading in the data in a tidy format,
  
  2. a `fit_popr()` method: for fitting statistical models to said data,
  
  3. and a `plot_popr()` method for producing nice visualisations.
  
Typically, these functions are applied sequentially. 
  
This package also allows for conversions between different units. 
There is a function for converting between different units of distance and a function to
convert between different currencies.
   4. `convertDist()`: for converting between different units of distance
   
   5. `load_fx()`: function to load in Forex data
   
   6. `exchange_rate()`: loads in exchange rate for a particular date from last 180 days
   
   7. `exchange_plot()`: produces plots given exchange rate for last 180 days

This vignette aims to demonstrate a typical workflow of the `ST403FinalProject` package.


### Installation 

__ST403FinalProject__ will run in Windows, Mac OS X, or Linux. To install it you first need to install [R](https://cran.r-project.org/). Installing [RStudio](https://www.rstudio.com/) as a nice desktop environment for using R is also recommended.

Once in R you can type at the R command prompt:

```{r, eval=FALSE}
install.packages('devtools')
devtools::install_github('kfoley-01/ST403-final_Project')
```

to install the latest development version of the package from the __ST403FinalProject__ [GitHub page](https://github.com/kfoley-01/ST403-final_Project). 

In either case, if you then type:

```{r, eval=FALSE}
library(ST403FinalProject)
```

it will load in all the aforementioned __ST403FinalProject__ functions.

Some features may not yet be fully tested, and occasionally this version might be liable to break when it is in the process of being updated. If you find bugs or want to suggest new features please visit the [GitHub issues page](https://github.com/kfoley-01/ST403-final_Project/issues).


## `load_popr()`

This function loads in population data from for countries at different intervals.  The output will contain the a dataframe of the popultions and the geometry data. In the example below, data is returned in a tidy format.

```{r}
dat <- load_popr()
dat
```


## `fit_popr()`

A dedicated `fit_popr()` method is provided for objects returned by `load_popr()`. This function will fit the model indicated by the `continent` argument to data at the intervals specified by the `year1` and `year2` arguments. In the example below, a  model is fit to the continent of Africa data for years 2022 and 2020. 

```{r}
model1 <- fit_popr("Africa", "2022", "2020", popr = dat)
```

Here, the model is created to show the differences in populations in African countries between the years 2022 and 2020.

To instead fit a model to show the differences in populations in European countries between the years 2000 and 1970, the function could have been applied as follows:

```{r, eval=FALSE}
model2 <- fit_popr("Europe", "2000", "1970", popr = dat)
```

## `plot_popr()`

The `plot_popr()` method provided simply plots the output of the fitted model. Taking `model1` from above, a plot can be created simply by typing `plot_popr(model1)`.

```{r, echo=FALSE}
plot_popr(model1)
```

The output of the plot function - a nice plot.

## `convertDist()`

The `convertDist()` function will convert from a one unit of distance to another,
with both the starting unit and ending unit being provided as parameters in 
the function call.

```{r, echo=FALSE}
convertDist(200,"meter","centimeter")
```

## Exchange {.tabset}

The exchange family of methods in this package aim to return exchange rates for given currencies and plot these exchange rates. 

 1.  Below is an example where USD is converted to GBP.

```{r}
100*exchange_rate("USD","GBP")
100*exchange_rate("USD","GBP","2022-11-01")
```
  We see here at the time of writing 100$ equates to roughly 82.91£ but on the first of November was 86.93£. Note the date format yyyy-mm-dd and also be aware the data is only available for last 180 days.
  
  2.  If looking to see overall trend between two currencies we can use *exchange_plot*
  
```{r,fig.width=5.5,fig.height=4}
exchange_plot("USD","GBP")
```
  
   The lines indicate the min,median and max for the given exchange rate. The current exchange rate is also given in the title
  
  3.
To access this data in the form of a data frame to do your own analysis use function *load_fx*

```{r}
df1<-load_fx(rates_list = c("EUR/USD","EUR/GBP","EUR/AUD","EUR/NZD"))
df1<-df1[order(df1$Date,df1$rate,df1$Index,decreasing = T),]
head(df1,n=8)
```

